IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/abstract.tex

\begin{abstract}
    Many important security problems in JavaScript, including extension
    security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
    XXX~\tocite{}, could be solved with a implementation
    of information flow control.  However, designing an IFC system which
    can be \emph{efficiently} implemented is quite a challenge.  In this paper,
    we formally describe a coarse-grained IFC system which fulfills this
    criterion.  The key idea is that an efficient IFC system must not
    depend too much on the details of the language it is integrated
    with.  The result is a general method for adding IFC to existing
    languages which is indifferent to the choice of language.
    Additionally, we describe how to relate concrete implementations
    with the IFC systems produced by our technique and show how various
    proposed and existing IFC systems fit into our formal framework.
\end{abstract}

>>>>

\begin{abstract}
    Many important security problems in JavaScript, such as browser extension
    security~\tocite{}, untrusted JavaScript libraries~\tocite{} and
    safe integration of mutually distrustful websites (mash-ups)~\tocite{}, may be effectively addressed using an efficient implementation
    of information flow control.
We present a coarse-grained IFC system that
can be implemented  non-intrusively, resulting in
much greater implementation efficiency than previous finer-grained approaches.
The central concept is an isolation mechanism whose operation does not
depend too much on the details of the programming language used.
We thus present a \emph{general} method for adding IFC to existing
languages that is largely \emph{indifferent} to the choice of language.
Additionally, we describe how to relate optimized concrete implementations
to the IFC systems produced by our technique and show how various
proposed and existing IFC systems conform to our formal framework
and therefore enjoy the semantic properties we prove.
\end{abstract}

### 2014-03-02 paper/formal.tex

In this section, we present the formal security guarantees provided by
our embedding.
%
Concretely, we show that |specLang alpha targetLang|, with an appropriate
scheduler |alpha|, satisfies non-interference~\cite{Goguen82},
without making any reference to properties of |targetLang|.
%
The precise scheduling policy dictates
what guarantee we can achieve for programs with diverging tasks.
For a sequential scheduler |seqf|, we will only be able to show
\emph{termination-insensitive non-interference}, where a program
may diverge based on secret data; this allows attackers to observe
secrets by observing the termination of tasks.
For the concurrent round-robin schedule |roundrobinf|,
we can show a stronger result known as
\emph{termination-sensitive non-interference},
where termination attacks cannot leak information.

How can we characterize what the \emph{secret inputs} of a program are?  Like
other work~\cite{Li+:2010:arrows,Russo+:Haskell08,lio,stefan:addressing-covert},
we specify and prove non-interference using \emph{term erasure}.
%
Intuitively, term erasure allows us to show that an attacker does not learn
any sensitive information from a program if the program behaves identically
(from the attacker point of view) to a program with all sensitive data
``erased''.
%
To accommodate for this, we extend our formalism with a function |erasef l| that
performs erasures by mapping configurations to erased configurations,
usually by rewriting (parts of) configurations that are more sensitive
than |l| to a new syntactic construct |bullet|.
%
In order for us to state non-interference, a language needs to include an
erasure function:

%\Red{should be the environment colored in the definition?}
%EZY: No, I don't think so.
\begin{definition}[Information flow control language]
    An information flow control language |L| is a tuple |(C, .->,
    erasef l)|, where $|C|$ is the type of machine configurations (members
    of which are usually denoted by the meta-variable |c|), |.->| is a
    reduction relation between machine configurations and |erasef l : C -> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  Sometimes, we refer as |V| to set of
     terminal configurations in |C|, i.e., configurations states where
     no further transitions are possible.
\end{definition}

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Our language |specLang alpha (targetLang nop)| can be
represented as |(ifc C, .->, erasef il)|, such that
$|ifc C| = |iS| \times \prod |it|$.  Here,
$|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|, and Figure~\ref{fig:erasure} gives the precise definition for
our erasure function |erasef il|.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|.
Otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

The definition of |erasef il| is quite important, as it captures the IFC
language's attacker model: elements that are erased cannot be observed
by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\cite{Castellani:Boudol:ICALP01,
stefan:addressing-covert}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\cite{yangresource}.
  %
  We leave this extension to future work.
}

Non-interference relies on the definition of an attacker's observational power at
security level |l|, which is typically defined as an equivalence
relation---called |l|-equivalence---on configurations.  An attacker
at level |l| cannot
distinguish two configurations that are |l|-equivalent.
%
Since our erasure function captures the attacker model, we simply define this
equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
    if |erase l c = erase il c'|.
\end{definition}
%

Intuitively, we can now state that a language satisfies non-interference if an
attacker at level |l| cannot distinguish the runs of any two |l|-equivalent
configurations.
%
This precise non-interference property is called termination sensitive non-interference
(TSNI).  Besides the obvious requirement to not leak secret information
to public channels, this definition also requires the termination
of public tasks to be independent of secret tasks.
%
Formally, we define TSNI as follows.

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language |(C, .->, erasef l)| is termination
  sensitive non-interfering if for any label |l|, and configurations
  |c1, c1', c2 member C|, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration |c2' member C| such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}
%
In other words if we take two |l|-equivalent configurations, then for every
intermediate step taken by the first configuration, there is a corresponding
number of steps that the second configuration can take to result in a
configuration that is |l|-equivalent to the first resultant configuration.

We now show that our IFC language satisfies TSNI %under a particular
%scheduling policy.
%
%Specifically, we consider the language 
under the round-robin scheduler
|roundrobinf| given in Figure~\ref{fig:scheduler}.

@@

In general TSNI will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha targetLang| with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
%
%In Section~\toref{} we detail the preceise scheduler for which our
%specification language is TSNI.
%

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI.
%
Concretely, consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
\Red{Ale: |when| was not defined, so I changed it to if-then-else}
These two configurations are |pub|-equivalent, but |ic1| will reduce 
(in two steps) 
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{sec:extensions}.}
then the |sec| tasks's decision to diverge or not is directly leaked to a
public entity.

@@

As shown by compilers~\cite{jif,FlowCaml}, interpreters~\cite{JSFlow}, and
libraries~\cite{Russo+:Haskell08,lio}, TINI is useful for sequential
settings. We show that our IFC language with the sequential scheduling policy
|seqf| satisfies TINI.
%
\begin{theorem}[Sequential IFC language is TINI]
  \label{thm:seq-tini}
For any target language |targetLang|, |specLang seqf targetLang| satisfies TINI.
\end{theorem}

>>>>

We are interested in proving non-interference about many programming
languages.  This requires an appropriate definition of this notion
that is language agnostic, so in this section, we present a few
general definitions for what an information flow control language is
and what non-interference properties it may have.  We also state
theorems about our system which we prove in Section~\ref{sec:proofs}.
In particular, we show that |specLang alpha targetLang|, with an appropriate
scheduler |alpha|, satisfies non-interference~\cite{Goguen82},
without making any reference to properties of |targetLang|.

\cut{
The precise scheduling policy dictates
what guarantee we can achieve for programs with diverging tasks.
For a sequential scheduler |seqf|, we will only be able to show
\emph{termination-insensitive non-interference}, where a program
may diverge based on secret data; this allows attackers to observe
secrets by observing the termination of tasks.
For the concurrent round-robin schedule |roundrobinf|,
we can show a stronger result known as
\emph{termination-sensitive non-interference},
where termination attacks cannot leak information.
}

\subsection{Erasure function}

When defining the security guarantees of an information flow control,
we must characterize what the \emph{secret inputs} of a program.  Like
other work~\cite{Li+:2010:arrows,Russo+:Haskell08,lio,stefan:addressing-covert},
we specify and prove non-interference using \emph{term erasure}.
%
Intuitively, term erasure allows us to show that an attacker does not learn
any sensitive information from a program if the program behaves identically
(from the attacker point of view) to a program with all sensitive data
``erased''.
%
To interpret a language under information flow control, we define a function |erasef l| that
performs erasures by mapping configurations to erased configurations,
usually by rewriting (parts of) configurations that are more sensitive
than |l| to a new syntactic construct |bullet|.  We can the define
an information flow control language as follows:

\begin{definition}[Information flow control language]
    An information flow control language |L| is a tuple |(C, .->,
    erasef l)|, where $|C|$ is the type of machine configurations (members
    of which are usually denoted by the meta-variable |c|), |.->| is a
    reduction relation between machine configurations and |erasef l : C -> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  Sometimes, we refer as |V| to set of
     terminal configurations in |C|, i.e., configurations states where
     no further transitions are possible.
\end{definition}

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Our language |specLang alpha (targetLang nop)| fulfills
this definition as|(ifc C, .->, erasef il)|, where
$|ifc C| = |iS| \times \prod |it|$.  The set of terminal conditions
$|ifc V|$ is $|iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|, and Figure~\ref{fig:erasure} gives the precise definition for
our erasure function |erasef il|.
%
Essentially, a task and its corresponding message queue is completely erased from the task
list if its label does not flow to the attacker observation level |il|.
Otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

The definition of an erasure function is quite important: it captures
the attack model, stating what can and cannot be observed by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\cite{Castellani:Boudol:ICALP01,
stefan:addressing-covert}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\cite{yangresource}.
  %
  We leave this extension to future work.
}

\subsection{Non-interference}

Given an information flow-control language, we can now define non-interference.
Intuitively, we want to make statements about the attacker's observational
power at some security level |l|.  This is done by defining an equivalence
relation called |l|-equivalence on configurations: an attacker should
not be able to distinguish two configuration that are |l|-equivalent.
%
Since our erasure function captures what an attacker can or cannot observe, we simply define this
equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
    if |erase l c = erase il c'|.
\end{definition}
%

We can now state that a language satisfies non-interference if an
attacker at level |l| cannot distinguish the runs of any two |l|-equivalent
configurations.
%
This particular property is called termination sensitive non-interference
(TSNI).  Besides the obvious requirement to not leak secret information
to public channels, this definition also requires the termination
of public tasks to be independent of secret tasks.
%
Formally, we define TSNI as follows:

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language |(C, .->, erasef l)| satisfies termination
  sensitive non-interference if for any label |l|, and configurations
  |c1, c1', c2 member C|, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration |c2' member C| such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}
%
In other words if we take two |l|-equivalent configurations, then for every
intermediate step taken by the first configuration, there is a corresponding
number of steps that the second configuration can take to result in a
configuration that is |l|-equivalent to the first resultant configuration.

Our IFC language satisfies TSNI %under a particular
%scheduling policy.
%
%Specifically, we consider the language 
under the round-robin scheduler
|roundrobinf| given in Figure~\ref{fig:scheduler}.

@@

In general, however, non-interference will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha targetLang| with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will in general break non-interference~\cite{Russo:Sabelfeld:CSFW06,BartheRRS07}.
%
%In Section~\toref{} we detail the preceise scheduler for which our
%specification language is TSNI.
%

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI:
%
consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, but |ic1| will reduce 
(in two steps) 
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{sec:extensions}.}
then the |sec| tasks's decision to diverge or not is directly leaked to a
public entity.

@@

As shown by compilers~\cite{jif,FlowCaml}, interpreters~\cite{JSFlow}, and
libraries~\cite{Russo+:Haskell08,lio}, TINI is useful for sequential
settings. In our case, we show that our IFC language with the sequential scheduling policy
|seqf| satisfies TINI.
%
\begin{theorem}[Sequential IFC language is TINI]
  \label{thm:seq-tini}
For any target language |targetLang|, |specLang seqf targetLang| satisfies TINI.
\end{theorem}

### 2014-03-02 paper/retrofit.tex

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|),
    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (a task can only increase its label, and not decrease it),
    \item Operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
        which interact with the global store of per-task message queues |iS|, and
    \item A sandboxing operation allowing to spawn new
    isolated tasks, described in more detail in the
    next section.
\end{itemize}

@@

At a high level, the semantics define a coarse-grained floating-label IFC
system~\cite{Zeldovich:2006, lio}, i.e., a system in which the current label of
the task can be raised to protect everything in scope.
%
We note that while first class labels and operations for inspecting the current
label are are essentially universal to all floating-label systems, our choice
of communication and isolation primitives is motivated by those present in
browsers, namely \texttt{postMessage} and Workers~\cite{webworkers,webmessaging}.
%
Of course, other choices such as blocking communication or labeled channels are
possible and further discussed in Section~\ref{sec:extensions}.
%
Though motivated by Web Workers, our notion of a task generalizes previous
primitives considered by floating-label dynamic IFC
systems~\cite{Zeldovich:2006, lio, stefan:addressing-covert,
Hritcu:2013:YIB:2497621.2498098}.

@@

\subsection{The embedding}

\Red{TODO[ds]:
  - clarify discussion on exceptions
  - fix the toLabled
}
Finally, in Figure~\ref{fig:embedding},
we provide all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

@@

@@

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
    \item We reinterpret |CE| to be evaluation contexts on task pools, providing definitions for |curlyRedE| and |curlyBlueE|.  These rules only operate on the first task in the task pool, which by convention is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task pools.  The correspondence is simple: a task executes a step and then is rescheduled in the task pool according to schedule policy |alpha|.  Not all schedulers preserve non-interference, and we provide two specific schedules in Figure~\ref{fig:scheduler}.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
    and intermediating between the borders of the two languages.
\end{itemize}

The \textsc{I-sandbox} rule allows to create a new isolated task that
executes separately from the existing tasks (and can be communicated
with via |send| and |recv|).  When the new task is created, there
is the question of what the target language state of the new task should
be.  Our rule is stated generically in terms of a function |klone|.
Conservatively, |klone| may be simply thought of as the identity
function, in which
case the semantics of sandbox are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of |klone|, but all our
non-interference claims will hold regardless of the choice of |klone|.

We note that it is possible to add rules for a natural embedding of
expressions that occur in both languages.  In our specific example
with |targetLangML|, we can choose to preserve booleans across
language boundaries as follows:
\begin{mathpar}
\inferrule[I-bool]
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule[T-bool]
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}

For any target language |targetLang| and scheduling policy |alpha|, this
embedding defines an information flow control language, which we will
refer to as |specLang alpha targetLang|.

@@

To get a feeling for how these operational semantics operate, we
would like to
describe a few sample programs, and what their outputs are.

@@

At first glance, it does not appear that our system has any such operator;
there are only tasks, and the correct behavior for a task throwing
an exception is self-evident: it should simply be removed from the scheduler.
However, under a \emph{sequential scheduler} (such as |seqf|),
the behavior of |sandbox|
can be used to model the behavior of such an operator:
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId; | \\
    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
When the sequential scheduler is used, the sandboxed task runs to
completion before returning to the task that sandboxed it.  Thus,
a task pool should rather be interpreted as a number of information flow
aware stack frames.  To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
channel, we might mix up our messages.  Indeed, a proper development requires
the ability to allocate fresh channels; for purposes of simplicity, this
has been omitted.}

>>>>

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|),
    \item Operations for inspecting (\textbf{getLabel}) and modifying (\textbf{setLabel}) the current label of the task (since the current label's role is to protect everything in the task, the task can only increase its label),
    \item Operations for non-blocking inter-task communication (\textbf{send} and \textbf{recv}),
        which interact with the global store of per-task message queues |iS|, and
    \item A sandboxing operation allowing to spawn new
    isolated tasks, described in more detail in the
    next section.
\end{itemize}

@@

At a high level, the semantics define a coarse-grained floating-label IFC
system~\cite{Zeldovich:2006, lio}, i.e., a system in which the current label of
the task can be raised to protect everything in scope;
%
this is different from traditional fine-grained language-based IFC systems that
associate labels with values~\cite{sabelfeld2003language,Austin:Flanagan:PLAS09}.
%
We note that while first class labels and operations for inspecting the current
label are are essentially universal to all floating-label systems, our choice
of communication and isolation primitives is motivated by those present in
browsers, namely \texttt{postMessage} and Workers~\cite{webworkers,webmessaging}.
%
Of course, other choices such as blocking communication or labeled channels are
possible and further discussed in Section~\ref{sec:extensions}.
%
Though motivated by Web Workers, our notion of a task generalizes previous
primitives considered by floating-label dynamic IFC
systems~\cite{Zeldovich:2006, lio, stefan:addressing-covert,
Hritcu:2013:YIB:2497621.2498098}.

@@

\subsection{The embedding}
Figure~\ref{fig:embedding}
provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

@@

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.
    %
In the target language, an IFC expression appears as |TI ie| (``target-outside,
IFC-inside''); in the IFC language, a target language expression appears as |IT
te| ( ``IFC-outside, target-inside'').
    \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.  These rules only operate on the first task in the task list, which by convention is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task lists.  The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|;
    Figure~\ref{fig:scheduler} defines two concrete schedulers.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
    and intermediating between the borders of the two languages.
\end{itemize}

@@

The \textsc{I-sandbox} rule is used to create a new isolated task that
executes separately from the existing tasks (and can be communicated
with via |send| and |recv|).  When the new task is created, there
is the question of what the target language state of the new task should
be.  Our rule is stated generically in terms of a function |klone|.
Conservatively, |klone| may be simply thought of as the identity
function, in which
case the semantics of sandbox are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of |klone|, but all our
non-interference claims will hold regardless of the choice of |klone|.

%
As in~\cite{Matthews:2007:OSM:1190216.1190220}, rules \textsc{T-border} and
\textsc{I-border} define the syntactic boundaries between the IFC and target
languages.
%
Intuitively, the boundaries respectively correspond to an upcall into and
downcall from the IFC runtime.
%

We note that it is possible to add rules for a natural embedding of
expressions that occur in both languages.  In our specific example
with |targetLangML|, we can choose to preserve booleans across
language boundaries as follows:
\begin{mathpar}
\inferrule
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}

For any target language |targetLang| and scheduling policy |alpha|, this
embedding defines an IFC language, which we will
refer to as |specLang alpha targetLang|.

@@

To get a feeling for how these operational semantics operate, we
describe a few sample programs, and their corresponding outputs.

@@

At first glance, it does not appear that our system has any such operator;
there are only tasks, and the correct behavior for a task throwing
an exception is self-evident: it should simply be removed from the scheduler.
However, under a \emph{sequential scheduler} (such as |seqf|),
the behavior of |sandbox|
can be used to model the behavior of such an operator:
\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId; | \\
    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
\end{align*}
When the sequential scheduler is used, the sandboxed task runs to
completion before returning to the task that sandboxed it.  Thus,
a task list should rather be interpreted as a number of information flow
aware stack frames.  To read the result of a |toLabeled| operation
(which is communicated via message passing), the parent task must raise
its label; otherwise the label will get dropped, as per the \textsc{I-recv} rule.\footnote{A keen reader may note that with a single, per-task
channel, we might mix up our messages.  Indeed, a proper development requires
the ability to allocate fresh channels; for purposes of simplicity, this
has been omitted.}
